What if you drop that? Modeling children's curiosity about physical interactions

### 2020-01-15 paper/paper.Rmd
some refs and basic outline

---
title: "Modeling children's intrinsically-motivated curiosity about object interactions"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

@@

@@

>>>>

---
#title: "Modeling children's intrinsically-motivated curiosity about object interactions"
title: "What if you drop that? Modeling children's curiosity about physical interactions"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

@@

the gap: major outstanding issue in the research on curiosity and exploratory play is the functional form of the intrinsic motivation

gold standard would be direct comparison of human and AI agents, but human behavior is so wide-ranging

we propose a new paradigm that enables

paragraph

@@

## Model subsection first

- or joint paradigm section
- developmental data collection
- model r

- simple statistical test (per drop / target set): 
chisq.test 
Observed vs Expected
